UCD\\MSc Thesis Proposal:\\\emph{An approach for Continuous Capacity Planning in Cloud Environments with Uptime-based Pricing Model}

### 2015-04-20 paper/paper.tex
more evaluation

\section{Structure of the Thesis}
\textbf{Background}. This section will outline the background information related to IaaS consumer challenges related to understanding the whole picture for price optimality of rented infrastructure. \par
\textbf{Design}. This section explains design and environment conditions for the algorithm to be useful. \par
\textbf{Implementation}. This section explains algorithm implementation details and data analytics software that was used - Apache Spark\footnote{\url{https://spark.apache.org}}. \par
\textbf{Evaluation}. The proposed algorithmic approach is applied to Google Trace data~\cite{clusterdata:Reiss2011}. \par
\textbf{Conclusion and Further Work}. The completed data analysis is discussed. Further work related to algorithm improvements, automation and lessons learned are presented.

@@

\begin{table}[h]
\begin{center}
    \begin{tabular}{| l | l |}
    \hline
    \textbf{Setting name} & \textbf{Value} \\
    \hline
    spark.master & local \\
    \hline
    spark.driver.memory & 8G \\
    \hline
    spark.executor.memory & 20G \\
    \hline
    spark.default.parallelism & 500 \\
    \hline
    \end{tabular}
\end{center}
\label{tab:spark_conf}
\caption{Apache Spark standalone cluster configuration settings}
\end{table}

@@

\begin{table}[h]
\begin{center}
    \begin{tabular}{| l | l | l | l |}
    \hline
    \textbf{Name} & \textbf{Scheme} & \textbf{Upfront (\$)} & \textbf{Per hour (\$)} \\
    \hline
    cc2.8xlarge & light & 1762 & 0.904 \\
    \hline
    cc2.8xlarge & medium & 4146 & 0.54 \\
    \hline
    cc2.8xlarge & heavy & 5000 & 0.361 \\
    \hline
    m2.4xlarge & light & 1088 & 0.676 \\
    \hline
    m2.4xlarge & medium & 2604 & 0.52 \\
    \hline
    m2.4xlarge & heavy & 3156 & 0.272 \\
    \hline
    \end{tabular}
\end{center}
\label{tab:aws_pricing}
\caption{AWS pricing for reserved cc2.8xlarge and m2.4xlarge instances}
\end{table}

\myparagraph{Usage data}
Google released 29 day cluster usage traces of more than 12k machines running over 650k jobs~\cite{clusterdata:Reiss2011}. As analyzed in ~\cite{clusterdata:Reiss2012b}

@@

\section{Calculate cph and ip}

@@

%%%%%%%%%%%%%%%%%%%%%%
%%% OPTIONAL!!!
%%% CAPACITY PLANNING 
%%% STRATEGIES    
%%%%%%%%%%%%%%%%%%%%%%

%\chapter{Capacity Planning Strategies}

%\section{Peak-to-mean ratio based resource assignment}

%\section{Only heavy instances}

%%%%%%%%%%%%%%%%%%%%%%
%%% CONCLUSION 
%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

\section{Structure of the Thesis}
\textbf{Background}. This section will outline the background information related to IaaS consumer challenges related to understanding the whole picture for price optimality of rented infrastructure. \par
\textbf{Design}. This section explains design and environment conditions for the algorithm to be useful. \par
\textbf{Implementation}. This section explains algorithm implementation details and data analytics software that was used - Apache Spark\footnote{\url{https://spark.apache.org}}. \par
\textbf{Evaluation}. The proposed algorithmic approach is applied to Google Trace data~\cite{clusterdata:Reiss2011}. \par
\textbf{Conclusion and Future Work}. The completed data analysis is discussed. Further work related to algorithm improvements, automation and lessons learned are presented.

@@

\begin{table}[h]
\begin{center}
    \begin{tabular}{| l | l |}
    \hline
    \textbf{Setting name} & \textbf{Value} \\
    \hline
    spark.master & local \\
    \hline
    spark.driver.memory & 8G \\
    \hline
    spark.executor.memory & 20G \\
    \hline
    spark.default.parallelism & 500 \\
    \hline
    \end{tabular}
\end{center}
\caption{Apache Spark standalone cluster configuration settings} 
\label{tab:spark_conf}
\end{table}

@@

\begin{table}[h]
\begin{center}
    \begin{tabular}{| l | l | l | l |}
    \hline
    \textbf{Name} & \textbf{Scheme} & \textbf{Upfront (\$)} & \textbf{Per hour (\$)} \\
    \hline
    cc2.8xlarge & light & 1762 & 0.904 \\
    \hline
    cc2.8xlarge & medium & 4146 & 0.54 \\
    \hline
    cc2.8xlarge & heavy & 5000 & 0.361 \\
    \hline
    m2.4xlarge & light & 1088 & 0.676 \\
    \hline
    m2.4xlarge & medium & 2604 & 0.52 \\
    \hline
    m2.4xlarge & heavy & 3156 & 0.272 \\
    \hline
    \end{tabular}
\end{center}
\caption{AWS pricing for reserved cc2.8xlarge and m2.4xlarge instances}
\label{tab:aws_pricing}
\end{table}

\myparagraph{Usage data}

Google released 29-day cluster usage traces of more than 12k machines running over 650k jobs~\cite{clusterdata:Reiss2011}. An analysis~\cite{clusterdata:Reiss2012b} revealed that the workload is heterogeneous, which is somewhat unique compared to other traces and makes a good fit for testing.
The trace contains data about jobs submitted by users. Each job is made of tasks. Each task reports metrics about resource consumption - e.g. CPU, memory - and timestamps. The trace does not contain information about the purpose of the jobs, which limits SLO assumptions to resource utilization. 
Resource utilization data is provided in normalized units - the strongest configuration is 1 and the rest of configurations are described in relation to that value.

@@

Google trace does not provide any information about pricing schemes of included machines. For evaluation purposes, we will produce example configurations of different pricing schemes that could exist within a real cluster.

The majority of machines within Google cluster i.e. 82\%, have following configuration: 0.5 CPU, 0.5 RAM or 0.5 CPU, 0.25 RAM. We will assign heavy pricing scheme for these machines. For the rest of the cluster, we will assign medium pricing scheme.

The light scheme is a good fit for relatively short periods of time, e.g. during peak. An analysis of the trace~\cite{clusterdata:Reiss2012b} shows that jobs with the highest peak-to-mean ratio are production priority jobs and they constitute only 7\% of all jobs. Therefore, we will not assign any light pricing schemes for this evaluation purposes.

We will refer to cc2.8xlarge and m2.4xlarge reserved instances pricing data as \textit{Scheme 1} and \textit{Scheme 2}.

\section{Pricing data indicators}

\subsection{Cost per hour}
\myparagraph{Scheme1}
\begin{table}[h]
\begin{center}
    \begin{tabular}{| l | l | l | l |}
    \hline
    \textbf{Hour} & \textbf{Light (price/hour)} & \textbf{Medium (price/hour)} & \textbf{Heavy (price/hour)} \\
    \hline
	1&5.7313972602739724&11.898904109589042&14.059630136986302 \\
    \hline
	2&3.317698630136986&6.2194520547945205&7.21031506849315 \\
    \hline
	3&2.513132420091324&4.326301369863014&4.9272100456621 \\
    \hline
	4&2.110849315068493&3.3797260273972602&3.785657534246575 \\    
	\hline
5&1.8694794520547946&2.811780821917808&3.1007260273972603 \\
	\hline
6&1.7085662100456622&2.433150684931507&2.64410502283105 \\
	\hline 
7&1.593628180039139&2.162700587084149&2.317947162426614 \\
\hline 
8&1.5074246575342467&1.9598630136986301&2.0733287671232876 \\
\hline
9&1.4403774733637749&1.8021004566210044&1.8830700152207003 \\
\hline
10&1.3867397260273973&1.6758904109589041&1.73086301369863 \\ 
\hline
11&1.342854296388543&1.5726276463262765&1.6063300124533002 \\ 
\hline
12&1.3062831050228312&1.4865753424657535&1.5025525114155251 \\
\hline
13&1.2753382507903057&1.4137618545837725&1.414740779768177 \\
\hline
14&1.2488140900195697&1.3513502935420745&1.3394735812133072 \\
\hline
15&1.2258264840182649&1.2972602739726027&1.2742420091324203 \\
\hline
16&1.2057123287671234&1.249931506849315&1.2171643835616437 \\
\hline
17&1.1879645447219984&1.208170829975826&1.1668017727639 \\
\hline
18&1.1721887366818875&1.1710502283105022&1.12203500761035 \\ 
\hline
19&1.1580735400144198&1.1378370583994233&1.0819805335255948 \\
\hline
20&1.1453698630136988&1.107945205479452&1.045931506849315 \\
\hline
21&1.1338760600130462&1.0809001956947162&1.0133157208088714 \\
\hline
22&1.1234271481942715&1.0563138231631384&0.9836650062266501 \\
\hline
23&1.1138868374032165&1.0338653960690887&0.9565926146515782 \\ 
\hline
24&1.1051415525114157&1.0132876712328769&0.9317762557077626 \\ 
    \hline
    \end{tabular}
\end{center}
\caption{cph results for cc2.8xlarge reserved instance}
\label{tab:cph:scheme1}
\end{table}

\myparagraph{Scheme2}

\begin{table}[h]
\begin{center}
    \begin{tabular}{| l | l | l | l |}
    \hline
    \textbf{Hour} & \textbf{Light (price/hour)} & \textbf{Medium (price/hour)} & \textbf{Heavy (price/hour)} \\
    \hline
1&3.656821917808219&7.654246575342467&8.918575342465754\\ 
 \hline 
2&2.1664109589041094&4.087123287671233&4.595287671232876\\ 
 \hline 
3&1.669607305936073&2.898082191780822&3.1541917808219178\\ 
 \hline 
4&1.4212054794520548&2.303561643835616&2.4336438356164383\\ 
 \hline 
5&1.2721643835616436&1.9468493150684931&2.0013150684931507\\ 
 \hline 
6&1.1728036529680366&1.709041095890411&1.713095890410959\\ 
 \hline 
7&1.1018317025440314&1.5391780821917809&1.5072250489236791\\ 
 \hline 
8&1.0486027397260274&1.411780821917808&1.352821917808219\\ 
 \hline 
9&1.0072024353120244&1.3126940639269407&1.2327305936073059\\ 
 \hline 
10&0.9740821917808219&1.2334246575342467&1.1366575342465755\\ 
 \hline 
11&0.9469838107098382&1.1685678704856788&1.058052303860523\\ 
 \hline 
12&0.9244018264840183&1.1145205479452056&0.9925479452054796\\ 
 \hline 
13&0.9052939936775553&1.0687881981032665&0.9371211801896734\\ 
 \hline 
14&0.8889158512720158&1.0295890410958906&0.8896125244618396\\ 
 \hline 
15&0.8747214611872147&0.9956164383561644&0.8484383561643836\\ 
 \hline 
16&0.8623013698630138&0.9658904109589042&0.8124109589041095\\ 
 \hline 
17&0.8513424657534246&0.9396615632554393&0.7806220789685737\\ 
 \hline 
18&0.8416012176560121&0.9163470319634702&0.7523652968036529\\ 
 \hline 
19&0.8328853640951694&0.8954866618601299&0.7270829127613554\\ 
 \hline 
20&0.825041095890411&0.8767123287671232&0.7043287671232877\\ 
 \hline 
21&0.8179439008480104&0.8597260273972603&0.6837416829745597\\ 
 \hline 
22&0.8114919053549191&0.8442839352428394&0.6650261519302615\\ 
 \hline 
23&0.8056009529481835&0.8301846337105421&0.6479380583680763\\ 
 \hline 
24&0.8002009132420091&0.8172602739726028&0.6322739726027398 \\
 \hline

    \end{tabular}
\end{center}
\caption{cph results for m2.4xlarge reserved instance}
\label{tab:cph:scheme1}
\end{table}

\subsection{Intersection points}
\myparagraph{Scheme1}
Intersection points:
Light/medium : 17
Medium/heavy : 13
Light / heavy : 16
\myparagraph{Scheme2}
Intersection points:
Light/medium : Never (surprisingly medium is never cheaper than light)
Medium/heavy : 6
Light / heavy : 14

@@

%%%%%%%%%%%%%%%%%%%%%%
%%% CONCLUSION AND 
%%% FUTURE WORK
%%%%%%%%%%%%%%%%%%%%%%

@@

\myparagraph{Conclusion}
It works and is great!

\myparagraph{Future Work}
\begin{enumerate}
\item Visual recognition of underperforming machines
\item Prediction trend to generate suggestions
\end{enumerate}
